\textbf{EECS 340: Assignment 2}

### 2020-02-03 assignment_2/article.tex
🐛 Correct Problem 1(b2).
🐛 Correct Problem 1(d1).

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(b2) If $f(n) \geq 1$, then $f(n) + c = O(f(n))$.}

Please refer to proof at \textbf{b1} as it provides a broader proof base on $f(n)$ regardless $f(n) \geq 1$ or not.

@@

Since $n \geq n_{0}$ by defination, and known that $g(n) \geq 1$ due to $\log(g(n)) \geq 0$; therefore there must be $g(n) \geq g(n_{0})$. Putting this into the context of \textit{Equation 10}, we may have:

@@

Since it is known that $f(n) \geq 0$, $g(n) \geq 0$, and $c > 0$; we must have a constant $c' > 0$ which satisfy:

\paragraph{Case 1} Assume $f(n) \neq 0$.

\begin{gather}
    c' \geq \frac{f(2n)}{f(n)} \\
    \Rightarrow f(2n) \leq c'(f(n))
\end{gather}

Thus we may conclude $f(2n) = O(f(n))$.

Similarly, we may also have a constant $c'' > 0$ which satisfy:

\begin{gather}
    c'' \leq \frac{f(2n)}{f(n)} \\
    \Rightarrow f(2n) \geq c''(f(n))
\end{gather}

Thus we may conclude $f(2n) = \Omega(f(n))$.\newline

Since both the $O$- and $\Omega$-notation are established, we may therefore conclude $f(2n) = \Theta(f(n))$ in this case.

\paragraph{Case 1} Assume $f(n) = 0$ for $\all n$.

Thus we must have two constants $k_{1}, k_{2}$ which satisfy:
\begin{gather}
    f(2n) = 0 \\
    k_{1}(0) \leq f(2n) \leq k_{2}f(n)\Rightarrow k_{1}(0) \leq 0 \leq k_{2}(0), \ \forall k \in \mathbb{R^+}
\end{gather}

Thus we may conclude $f(2n) = \Theta(f(n))$.\newline

Since both cases reach to the conclusion of $f(2n) = \Theta(f(n))$, we have proven the statement to be valid.

\subsection{(d2) If $f(n) = O(n^c)$, then $f(2n) = O(n^c)$}

@@

\subsection{(d3) If $f(n) = \Theta(n^c)$, then $f(2n) = \Theta(f(n))$}
Please refer to proof at \textbf{d3} as it provides a broader proof base on $f(n)$ regardless $f(n) = \Theta(n^c)$ or not.

>>>>

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(b2) If $f(n) \geq 1$, then $f(n) + d = O(f(n))$.}

According to the defination of $O$-notation, we have:

\begin{gather}
 f(n) = O(f(n)) \nonumber\\
 \exists c, n_{0} > 0 \ \text{ s.t.  $0 \leq f(n) \leq cf(n)$ \ \ \ for $n \geq n_{0}$} \\
 \exists n' > 0 \ \text{ s.t.  $f(n) \geq f(n')$ \ \ \ for $n, n' \geq n_{0}$} \\
 \Rightarrow 0 \leq f(n)+d \leq cf(n) + d \ \ \ \text{for $n \geq n_{0}$}
\end{gather}

Thus, we may rewrite the above equation as:

\begin{gather}
 0 \leq f(n)+d \leq (c + \frac{d}{f(n)})f(n) \ \ \ \text{for $f(n) \geq 1$} \nonmumber\\
 \Rightarrow 0 \leq f(n)+d \ \leq \ c'f(n) \ \ \ \text{for } \begin{cases}
                 c' = c + \frac{d}{f(n')} \\
                 n, n' \geq n_{0}
             \end{cases}
\end{gather}

Therefore, we may conclude if $f(n) \geq 1$, then $f(n) + d = O(f(n))$ via direct proof.

@@

Since $n \geq n_{0}$ by defination, and known that $g(n) \geq 1$ due to $\log(g(n)) \geq 0$; therefore there must be $g(n) \geq g(n_{0})$. Putting this into the context of \textit{Equation 12}, we may have:

@@

For $f(n) = 2^n$, we have $f(2n) = 4^n$. Where $f(2n) \neq \Theta(f(n))$ due to the LHS has a higher asymptotic order, and therefore we can't find any constant $c_{1}, c_{2}$ to form a relation of $c_1 \cdot 2^n \leq 4^n \leq c_2 \cdot 2^n$. Thus, the statement is invalid.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(d2) If $f(n) = O(n^c)$, then $f(2n) = O(n^c)$}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(d3) If $f(n) = \Theta(n^c)$, then $f(2n) = \Theta(f(n))$}
Please refer to proof at \textbf{d3} as it provides a broader proof base on $f(n)$ regardless $f(n) = \Theta(n^c)$ or not.
